\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2015-09-23 ACC16.2.tex
finished proof of adaptive control

This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
However, this does not necessarily show that \( R \to R_d \) as \( t \to \infty \). 
There are three additional critical points of \( \Psi \) where \( e_R = 0 \).
At an undesired equilibrium \( R = \exp{\pi \hat{e}_i} R_d \) and \( e_\Omega =0 \). 
This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
At any of these undesired equilibria we have \( V = k \). 
We define an augmented Lyapunov function as
\begin{align*}
	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R (\frac{k}{k_R}+ \Psi(R,R_d)) \, .
\end{align*}
We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \pi \hat{e}_i} R_d \) such that the \( k_r \parenth{\frac{k}{k_R}+\Psi }> 0 \).
This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
According to Chateav's theorem the undesired equilibria are unstable~\cite{khalil1996}.
As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable.

@@

Lyapunov analysis which shows that it's stable

Adaptive update law and control input

Add the disturbance term and introduce adaptive update law

>>>>

This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
However, this does not necessarily show that \( R \to R_d \) as \( t \to \infty \). 
There are three additional critical points of \( \Psi \) where \( e_R = 0 \).
At an undesired equilibrium \( R = \exp{\pi \hat{e}_i} R_d \) and \( e_\Omega =0 \). 
This results in \( A \) having a value of \( g_1 + g_2, g_2 + g_3 \) or \( g_3 + g_1 \).
At any of these undesired equilibria we have \( V = k \). 
We define an augmented Lyapunov function as
\begin{align*}
	W = k - V = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \parenth{\frac{k}{k_R}+ \Psi(R,R_d)} \, .
\end{align*}
We can choose an attitude \( R \) arbitrarily close to the equilibrium point \( \exp{ \pi \hat{e}_i} R_d \) such that the \( k_r \parenth{\frac{k}{k_R}+\Psi }> 0 \).
This is due to the fact that \( \Psi \) is positive definite about \( R = R_d \) as shown in~\cref{item:prop_psi_psd}.
If \( e_\Omega \) is sufficiently small this results in \( W > 0 \) and \( \dot{W} = -\dot{V} > 0\) from~\cref{eqn:vdot_nodist}.
According to Chateav's theorem the undesired equilibria are unstable~\cite{khalil1996}.
As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable.

@@

\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
Given  a desired attitude command \( R_d, \Omega_d = 0 \) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for \( \bar{\Delta} \) as follows:
\begin{align}
	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} \, , \label{eqn:adaptive_control} \\
	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} \, . \label{eqn:delta_dot}
\end{align}
If \( c \) is chosen such that
\begin{gather}
	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k-R \lambda_M H} \, , \label{eqn:c_bound}
\end{gather}
  the zero equilibrium of the error vectors \( e_R, e_\Omega\) are asymptotically stable.
\end{prop}
\begin{proof}[Proof of~\cref{prop:adaptive_control}]\label{proof:adaptive_control}
	Consider the Lyapunov function \( V \) given by
	\begin{gather}
		V = \frac{1}{2} e_\Omega J e_\Omega + k_R \Psi + c J e_\Omega^T e_R + \frac{1}{2 k_\Delta} e_\Delta^T e_\Delta \, , \label{eqn:v_adapt}
	\end{gather}
	over the domain \( D \) in~\cref{eqn:domain}.
	From~\cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
	\begin{gather}
		V \leq z^T W z \, , \label{eqn:v_upper_bound}
	\end{gather}
	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = \begin{bmatrix}{ccc}e_R & e_\Omega & e_\Delta\end{bmatrix} \) and the matrix \(W \in \R^{3 \times 3}\) is given by
	\begin{gather*}
		W = \begin{bmatrix}{ccc}
			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
			0 & 0 & \frac{1}{2 k_\Delta}
		\end{bmatrix} \, .
	\end{gather*}
	The time derivative of with the control inputs~\cref{eqn:adaptive_control} is defined as
	\begin{align}
		\dot{V} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} \, , \label{eqn:vdot}
	\end{align}
	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
	\begin{align*}
		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 \, . 
	\end{align*}
	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{V} \) is written as
	\begin{gather*}
		\dot{V} \leq -z^T M z \, ,
	\end{gather*}
	where the matrix \( M \in \R^{2 \times 2} \) is 
	\begin{gather}
		M = \begin{bmatrix}{cc}
			k_R c & \frac{k_\Omega c}{2} \\
			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
		\end{bmatrix} \, .
	\end{gather}
	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
	This implies that the zero equilibrium \( e_R, e_\Omega\) is asymptotically stable. 
\end{proof}

Local asymptotic stability

Domain avoids undesired equilibria
